Almost compatible functions and infinite length games

### 2015-11-25 articles/almost-compatible-functions-and-topological-games/article.tex
mark kurepa proof as unfinished

  \begin{proof}
    We use the family \(\mc K\) which is a base of \(\aleph_0\)-many compact
    open sets for each point in the constructed topology on
    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable, and the closure of every
    countable set is a compact countable set. Thus \(\mc K\)
    is cofinal in \([\omega_n]^\omega\).
    It is Kurepa since for every countable set \(A\), there are only countably
    many compact open sets in \(\mc K\)
    joined to \(A\) by a finite linked chain.
  \end{proof}

>>>>

  \begin{proof}
    We use the family \(\mc K\) of all compact
    open sets in the constructed topology on
    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
    a locally countable space is countable, and the closure of every
    countable set is a compact countable set; thus \(\mc K\)
    is cofinal in \([\omega_n]^\omega\).
    It is Kurepa since for every countable set \(A\), there are only
    countably many distinct compact open sets in \(\cl A\): TODO finish
  \end{proof}
